CuO Analysis Details

### 2019-05-31 paper/outline.tex
small changes to outline, got to get figures good

\documentclass{article}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage[margin=1.0in]{geometry}
\usepackage{float}

\begin{document}
\section{Introduction}
\begin{enumerate}
\item \textbf{General goal}
Systematically develop model Hamiltonians which can accurately describe the energies and properties of the lowest lying eigenstates for transition-metal oxide (TMO) molecules.

\item \textbf{Barrier to achieving that goal} The necessity for many-body interactions in describing the low-lying excited states of TMO molecules poses a difficult challenge when developing model Hamiltonians.

\item \textbf{State of the art} Common approaches to building these model Hamiltonians use effective single particle theories like Density Functional Theory (DFT) to generate an effective 1-body model or use the known energy spectrum of the TMO molecules to fit a model with many-body interactions. 
\textcolor{red}{Have to find references for this one, not sure how true this is.}

\item\textbf{How are we advancing state of the art} We have systematically developed a many-body model which can accurately describe energies and properties of the lowest lying eigenstates for the neutral CuO molecule using \textit{ab-initio} Quantum Monte Carlo (QMC) calculations and a density-matrix downfolding (DMD) procedure. 
\end{enumerate}

@@

\section{Conclusion}
\begin{enumerate}
\item \textbf{Our findings} We have systematically developed a many-body model which can accurately describe energies and properties of the lowest lying eigenstates for the neutral CuO molecule using \textit{ab-initio} Quantum Monte Carlo (QMC) calculations and a density-matrix downfolding (DMD) procedure.

\item \textbf{Avenues of interest} The procedure outlined here can be extended to other neutral transition metal oxide molecules, allowing for the construction of a sequence of low-energy models across the transition metals.
\end{enumerate}

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage[margin=1.0in]{geometry}
\usepackage{float}
\usepackage{ulem}

\begin{document}
\section{Introduction}
\begin{enumerate}
\item \textbf{General goal}
Systematically develop model Hamiltonians which can accurately describe the energies and properties of the lowest lying eigenstates for strongly correlated electrons systems.

\item \textbf{Barrier to achieving that goal} The necessity for many-body interactions in describing the low-lying excited states of strongly correlated electron systems poses a difficult challenge when developing model Hamiltonians.

\item \textbf{State of the art} Common approaches to building these model Hamiltonians use effective single particle theories like density functional theory (DFT) to generate an effective 1-body model or build phenomenological models based on experimental measurements of the properties and energies of low-lying excitations.
\textcolor{red}{Have to find references for this one, not sure how true this is.}

\item\textbf{How are we advancing state of the art} In this paper we systematically fit a many-body model which can accurately describe energies and properties of low-lying eigenstates for the neutral CuO molecule using a generalizable \textit{ab-initio} Quantum Monte Carlo (QMC) density matrix downfolding (DMD) method, and discuss the details of and developments in the model fitting procedure.
\end{enumerate}

@@

\section{Conclusion}
\begin{enumerate}
\item \textbf{Our findings} In this paper we systematically fit a many-body model for the neutral CuO molecule which can accurately reproduce the spectrum and properties of low-lying eigenstates seen in experiment using a \textit{ab-initio} Quantum Monte Carlo (QMC) density matrix downfolding (DMD) method, and discuss the details of and developments in our model fitting procedure.

\item \textbf{Avenues of interest} The fitting procedure illustrated here can be extended to other neutral transition metal oxide molecules, allowing for the construction of a sequence of low-energy models across the transition metals.
\end{enumerate}
